Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-10-15 icde2016/intro.tex
reworded the last sentence

In recent years, there has been a growth of interest in data visualization technologies for human-assisted data analysis using systems such as Polaris~\cite{Stolte:2008} and Spotfire~\cite{Ahlberg:1996}. While computers can provide high-speed and high-volume data processing, humans have both domain knowledge and the ability to process data in parallel by using our visual systems \vidya{need some references - perhaps Bill Cleveland's work or Jock's book}. Humans also provide the definition of what is valuable in an analysis. \vidya{Don`t really understand the point of this sentence:}Accordingly, hybrid human/computer analytic systems are essential to extracting knowledge of value to humans and their societies from the large amounts of data being generated today.

>>>>

In recent years, there has been a growth of interest in data visualization technologies for human-assisted data analysis using systems such as Polaris~\cite{Stolte:2008} and Spotfire~\cite{Ahlberg:1996}. While computers can provide high-speed and high-volume data processing, humans have both the domain knowledge and the ability to process data in parallel by using their visual systems \vidya{need some references - perhaps Bill Cleveland's work or Jock's book}. Humans also provide the definition of what is valuable in an analysis. Algorithms that rely on \emph{both} the processing capability of computer systems and human feedback, are more effective in extracting useful knowledge from the large amounts of data being generated.
\vidya{still struggling to understand how interactivity is relevant to what we're doing here...}
